---
title: "Example from Fox and Weisberg"
author: "Jacob Weverka"
date: "7/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br/><br/>
<br/><br/>
<br/><br/>


<font size="4"> Serially Correlated Errors </font>

In time series data, errors from a  regression model are unlikely to be independent

  - assume that the process generating errors is stationary (need to figure out what this means)
  - need to figure out this math in general
  
<br/><br/>
  
<font size="4"> Using the gls Function </font>

The ``` gls() ``` function is from the nlme package

```{r, message = FALSE}
# install.packages("nlme")
# install.packages("car")
library(nlme)
library(tidyverse)
library(car)
```

Load some example data - Hartnagel - from the "car" package (Companion to Applied Regression) 

year, 1931–1968.

  - tfr, the total fertility rate, births per 1000 women-
  - partic, women’s labor-force participation rate, per 1000.
  - degrees, women’s post-secondary degree rate, per 10,000.
  - fconvict, women’s indictable-offense conviction rate, per 100,000.
  - ftheft, women’s theft conviction rate, per 100,000.
  - mconvict, men’s indictable-offense conviction rate, per 100,000.
  - mtheft, men’s theft conviction rate, per 100,000.
  

```{r}

head(Hartnagel)

```



Here's a first look on women's conviction rates through time

```{r}


p = ggplot(data = Hartnagel, aes(x = year, y = fconvict)) + 
  geom_point() +
  geom_line() +
  ylab("Convictions per 100,000 Women")

p
```


Preliminary Ordinary Least Squares regression
```{r}
mod.ols = lm(fconvict ~ tfr + partic + degrees + mconvict, data = Hartnagel)
summary(mod.ols, correlation = TRUE)
```

According to the OLS regression, Womxn's crime rate declines with fertility and increases with participation in the labor force

<br/><br/>

However, a graph of residuals shows that residuals may be autocorrelated:

```{r}
q = ggplot(data = Hartnagel, aes(x = year, y = residuals(mod.ols))) +
  geom_col()

q

```


We can compute and plot the autocorrelation and partial autocorrelation functions of a time series using the ```{r} acf() ``` function.

```{r}
acf(residuals(mod.ols))
acf(residuals(mod.ols), type = "partial")
```

We can follow this with the Durbin-Watson Test, which tests for autocorrelation

The function ```{r} durbinWatsonTest() ``` calculates bootstrapped p-values. Alternatively, ```{r} dwtest() ``` in the lmtest package conputes the p-value for the first order DW test analytically

```{r}
durbinWatsonTest(mod.ols, max.lag = 5)

lmtest::dwtest(mod.ols)

```
So there is autocorrelation in this model. 


Using the gls() function:

```{r}

mod.gls = gls(fconvict ~ tfr + partic + degrees + mconvict, data = Hartnagel, correlation = corARMA(p = 2), method = "ML")

summary(mod.gls)

```

Here, the correlation structure is specified as an AR(2) process 






















