---
title: "Example from Fox and Weisberg"
author: "Jacob Weverka"
date: "7/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br/><br/>
<br/><br/>
<br/><br/>


<font size="4"> Serially Correlated Errors </font>

In time series data, errors from a  regression model are unlikely to be independent

  - assume that the process generating errors is stationary (need to figure out what this means)
  - need to figure out this math in general
  
<br/><br/>
  
<font size="4"> Using the gls Function </font>

The ```{r} gls() ``` function is from the nlme package

```{r}
# install.packages("nlme")
library(nlme)
```

Load some example data from the "car" package (Companion to Applied Regression) 

```{r}
# install.packages("car")
library(car)

Hartnagel

```


year, 1931–1968.

  - tfr, the total fertility rate, births per 1000 women-
  - partic, women’s labor-force participation rate, per 1000.
  - degrees, women’s post-secondary degree rate, per 10,000.
  - fconvict, women’s indictable-offense conviction rate, per 100,000.
  - ftheft, women’s theft conviction rate, per 100,000.
  - mconvict, men’s indictable-offense conviction rate, per 100,000.
  - mtheft, men’s theft conviction rate, per 100,000.
  

Here's a first look on women's conviction rates through time

```{r}
# library(tidyverse)

p = ggplot(data = Hartnagel, aes(x = year, y = fconvict)) + 
  geom_point() +
  geom_line() +
  ylab("Convictions per 100,000 Women")
p
```


Preliminary Ordinary Least Squares regression
```{r}
mod.ols = lm(fconvict ~ tfr + partic + degrees + mconvict, data = Hartnagel)
summary(mod.ols)
```

According to the OLS regression, Womxn's crime rate declines with fertility and increases with participation in the labor force

<br/><br/>

However, a graph of residuals shows that residuals may be autocorrelated:

```{r}
q = ggplot(data = Hartnagel, aes(x = year, y = residuals(mod.ols))) +
  geom_point()

q
```
We can compute and plot the autocorrelation and partial autocorrelation functions of a time series using the ```{r} acf() ``` function.

```{r}
acf(residuals(mod.ols))
acf(residuals(mod.ols), type = "partial")
```












